---
title: "well_sem_prediction_analysis"
author: "Rachel Weng"
date: "5/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Planned analysis
1.The dependent variable is participants’ first looks on four objects:  
(1) relevant animal, (2) relevant instrument, (3) irrelevant animal, and (4) irrelevant instrument.
 
2.The model included random intercepts for participants and items, as well as random by-participant slopes for semantic predictability condition.

3.The condition was entered as a deviation coded contrast: semantically predictable condition (−0.50) vs. semantically unpredictable condition (0.50).

4.We will consider the task successfully replicated in principle if we observe a significant effect of the predictability in the first look.
## 19 participants

```{r,include=FALSE}
library(lme4)
library(lmerTest)
library(optimx)
library(Rmisc)
library(ggplot2)
library(ggsignif)
```

```{r, warning=FALSE}
Data <- read.csv("well_pred_firstlook_proportion.csv")
head(Data)
```


# Data summary table (N=19)
```{r, warning=FALSE}
df <- summarySE(Data, measurevar="mean", groupvars=c("look","cond"))
df
```

# Data visualization: Line plot 
```{r, warning=FALSE}
ggplot(df, aes(x = cond, y = mean, group = look)) +
  geom_line(aes(linetype = look), position = position_dodge(width = 0.1)) +
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se),
                width = .1, position = position_dodge(width = 0.1), linetype = 1) +
  geom_point(size = 3, position = position_dodge(width = 0.1), color = "black") +
  guides(linetype = guide_legend("Look Region")) +
  theme(
    panel.background = element_rect(fill = "white"),
    legend.key  = element_rect(fill = "white"),
    axis.line.x = element_line(colour = "black", size = 0.4),
    axis.line.y = element_line(colour = "black", size = 0.4)) + 
  labs(
    x = " ",
    y = "Proportion of first-look fixation on animal and instrument (%)")
```

# Data visualization: Bar plot
```{r, warning=FALSE}
ggplot(df, aes(x=look, y=mean, fill=cond)) + 
geom_bar(stat="identity", position = "dodge") +
geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.1, position = position_dodge(width = 0.9)) +
ylim(0, 0.4) +
xlab("Look regions") +
ylab("Percentage of First Fixation (%)") +
theme_classic(base_size = 13) +
scale_fill_manual(values=c("#E69F00", "#56B4E9"), guide = guide_legend(title = "Condition")) 
#facet_wrap(cond ~., ncol=1)
```

# Linear mixed model
```{r, warning=FALSE}
result <- lmer(mean ~ 1 + cond*look + (1|subject) + (1|cond), data = Data ,control = lmerControl(calc.derivs = FALSE))
summary(result)
```


