---
title: "well_vb_learning_analysis"
author: "Rachel Weng"
date: "5/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Planned analysis
1.The dependent variable is participants’ eye fixations on a target instrument or a target animal image.

2.The model included random intercepts for participants and items, as well as random by-participant slopes for verb bias condition, time window.

3.A successful replication will be considered to be obtained if we observe there is a significant difference in the proportion of fixations to either the target animal or the target instrument based on training conditions in the second and third time window.

```{r,include=FALSE}
library(lme4)
library(lmerTest)
library(optimx)
library(Rmisc)
library(ggplot2)
library(ggsignif)
```

```{r, warning=FALSE}
Data <- read.csv("well_train_firstlook_proportion.csv")
head(Data)
```

# Data summary table (N=19)
```{r, warning=FALSE}
df <- summarySE(Data, measurevar="mean", groupvars=c("look","cond","cond2"))
df
```

# Data visualization: Bar plot
```{r, warning=FALSE}
ggplot(df, aes(x=cond, y=mean, fill=look)) + 
geom_bar(stat="identity", position = "dodge") +
geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width = 0.1, position = position_dodge(width = 0.9))+
ylim(0, 0.8)+
xlab("Testing order") +
ylab("Percentage of First Fixation (%)") +
theme_classic(base_size = 14) +
scale_fill_manual(values=c("#E69F00", "#56B4E9"), guide = guide_legend(title = "Look region"))+
facet_wrap(cond2 ~ .)
```

# Linear mixed model
## 1. Instrument-biased training

### Contrast: Test order 1 vs Test order 2
```{r, warning=FALSE}
DataIn <- subset(Data, cond2!="mod_trained")
my.helmert = matrix(c(-1/2, 1/2, 0), ncol = 1) # Contrast: Test order 1 vs Test order 2
DataIn$cond <- as.factor(DataIn$cond)
contrasts(DataIn$cond) = my.helmert
resultIn <- lmer(mean ~ 1 + cond*look + (1 |subject) , data = DataIn, control = lmerControl(optimizer= "optimx", optCtrl=list(method="nlminb")))
summary(resultIn)
```

### Contrast: Test order 1 vs Test order 3
```{r, warning=FALSE}
DataIn <- subset(Data, cond2!="mod_trained")
my.helmert = matrix(c(-1/2, 0, 1/2), ncol = 1) # Contrast: Test order 1 vs Test order 3
DataIn$cond <- as.factor(DataIn$cond)
contrasts(DataIn$cond) = my.helmert
resultIn <- lmer(mean ~ 1 + cond*look + (1|subject), data = DataIn, control = lmerControl(optimizer= "optimx", optCtrl=list(method="nlminb")))
summary(resultIn)
```

### Contrast: Test order 2 vs Test order 3
```{r, warning=FALSE}
DataIn <- subset(Data, cond2!="mod_trained")
my.helmert = matrix(c(0, -1/2, 1/2), ncol = 1) # Contrast: Test order 2 vs Test order 3
DataIn$cond <- as.factor(DataIn$cond)
contrasts(DataIn$cond) = my.helmert
resultIn <- lmer(mean ~ 1 + cond*look + (1|subject), data = DataIn, control = lmerControl(optimizer= "optimx", optCtrl=list(method="nlminb")))
summary(resultIn)
```

## 2. Modifier-biased training

### Contrast: Test order 1 vs Test order 2
```{r, warning=FALSE}
DataAn <- subset(Data, cond2!="inst_trained")
my.helmert = matrix(c(-1/2, 1/2, 0), ncol = 1) # Contrast: Test order 1 vs Test order 2
DataAn$cond <- as.factor(DataAn$cond)
contrasts(DataAn$cond) = my.helmert
resultAn <- lmer(mean ~ 1 + cond*look + (1|subject), data = DataAn, control = lmerControl(optimizer= "optimx", optCtrl=list(method="nlminb")))
summary(resultAn)
```

### Contrast: Test order 1 vs Test order 3
```{r, warning=FALSE}
DataAn <- subset(Data, cond2!="inst_trained")
my.helmert = matrix(c(-1/2, 0, 1/2), ncol = 1) # Contrast: Test order 1 vs Test order 3
DataAn$cond <- as.factor(DataAn$cond)
contrasts(DataAn$cond) = my.helmert
resultAn <- lmer(mean ~ 1 + cond*look + (1|subject), data = DataAn, control = lmerControl(optimizer= "optimx", optCtrl=list(method="nlminb")))
summary(resultAn)
```

### Contrast: Test order 2 vs Test order 3
```{r, warning=FALSE}
DataAn <- subset(Data, cond2!="inst_trained")
my.helmert = matrix(c(0, -1/2, 1/2), ncol = 1) # Contrast: Test order 2 vs Test order 3
DataAn$cond <- as.factor(DataAn$cond)
contrasts(DataAn$cond) = my.helmert
resultAn <- lmer(mean ~ 1 + cond*look + (1|subject), data = DataAn, control = lmerControl(optimizer= "optimx", optCtrl=list(method="nlminb")))
summary(resultAn)
```
